Pre- and Post-Debate Democratic Primary Data: Twitter, Google Trends, and Polls

### 2019-12-08 Presentation/SURV727_FinalPresentation_Padgett_Thiam.Rmd
Update SURV727_FinalPresentation_Padgett_Thiam.Rmd

- Bullet 1
- Bullet 2
- Bullet 3

>>>>

- Used Rweet package and searh_tweet function with selected keywords to gather tweets between November 20th and November 21st
- Separated the 1.3 million tweets after removing irrelevant tweets in 2 groups: pre and post debate
- Generated maps by number of tweets per candidate and ran sentiment analysis for 5 candidates

```{r, include=FALSE}
#USE THIS CHUNK TO BRING IN props_tab1 and props_tab2
source_data("https://github.com/znpadgett/surv727_padgett_thiam/blob/master/Data/props_tab1.RData?raw=true")
source_data("https://github.com/znpadgett/surv727_padgett_thiam/blob/master/Data/props_tab2.RData?raw=true")
```

## Pre-debate number of tweets 
```{r, fig.cap="Pre-debate Mentions in Tweets, by Candidate"}
props_tab1 %>%
  filter(Cat == "TRUE") %>%
  ggplot() +
  geom_col(mapping = aes(x = reorder(Candidate, -Count), y=Count, fill = Candidate)) +
    labs(x = "Democatric Party Canditates", 
       y = "Number of Tweets", 
       caption = "Source: Twiiter") 
```

## Post-debate number of tweets 
```{r, fig.cap="Post-debate Mentions in Tweets, by Candidate"}
props_tab2 %>%
  filter(Cat == "TRUE") %>%
  ggplot() +
  geom_col(mapping = aes(x = reorder(Variable, -Count), y=Count, fill = Variable)) +
    labs(x = "Democatric Party Canditates", 
       y = "Number of Tweets", 
       caption = "Source: Twiiter")
